noam_data_exploration_v1

### 2024-07-22 noam_data_exploration_v3.Rmd
Continuing to add more vis options.

diversity_stability_quadrat <- 
  merge(diversity_stability_quadrat, lm_synchrony_quadrat, by = "Location") # add in loreau and de Mazancourt synchrony
diversity_stability_quadrat <- merge(diversity_stability_quadrat, gross_synchrony_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, quadrat_level_portfolio, by = "Location") # add in portfolio effects
diversity_stability_quadrat <- merge(diversity_stability_quadrat, variance_ratio_quadrat, by = "Location")
pairs(~ Cover_mean + Cover_cv + Cover_stability + 
        Shannon_mean + Shannon_cv + Shannon_stability + 
        Loreau_synchrony +  Portfolio_effect + VR, data = diversity_stability_quadrat)

>>>>

diversity_stability_quadrat <- 
  merge(diversity_stability_quadrat, lm_synchrony_quadrat, by = "Location") # add in loreau and de Mazancourt synchrony
diversity_stability_quadrat <- merge(diversity_stability_quadrat, gross_synchrony_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, quadrat_level_portfolio, by = "Location") # add in portfolio effects
pairs(~ Cover_mean + Cover_cv + Cover_stability + 
        Shannon_mean + Shannon_cv + Shannon_stability + 
        Loreau_synchrony + Gross_synchrony + Portfolio_effect, data = diversity_stability)
